---
title: "Business Forecasting Assignment"
author: "Deepthi JahanMohan"
date: "20/09/2025"
output: html_document
---
# Creating a Employee Survey

```{r}
```{r setup-libs, include=FALSE}
# Load required libraries
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

```{r setup, include=FALSE}
EmployeeSurvey <- read.csv("EmployeeSurvey.csv")



EmployeeSurvey

# Summary
summary(EmployeeSurvey)
```
summary(EmployeeSurvey)

```{r}
min(EmployeeSurvey$Age)
```
min(EmployeeSurvey$Age)

```{r}
max(EmployeeSurvey$Age)
```

max(EmployeeSurvey$Age)
```{r}
range(EmployeeSurvey$Age)
```

range(EmployeeSurvey$Age)
```{r}
str(EmployeeSurvey)
```
str(EmployeeSurvey)

```{r}
# Box Plot Columns

boxplot(EmployeeSurvey$Age)
```

boxplot(EmployeeSurvey$Age)
```{r}
boxplot(EmployeeSurvey$Gender)
```
boxplot(EmployeeSurvey$Gender)

```{r}
boxplot(EmployeeSurvey$JobSatisfaction)
```
boxplot(EmployeeSurvey$JobSatisfaction)

```{r}
boxplot(EmployeeSurvey$ImpCharacteristics)
```
boxplot(EmployeeSurvey$ImpCharacteristics)

```{r}
boxplot(EmployeeSurvey$YearsinJob)
```
boxplot(EmployeeSurvey$YearsinJob)

```{r}
boxplot(EmployeeSurvey$Promotion)
```
boxplot(EmployeeSurvey$Promotion)

```{r}
boxplot(EmployeeSurvey$DecisionMaking)
```
boxplot(EmployeeSurvey$DecisionMaking)

```{r}
boxplot(EmployeeSurvey$BudgetDecisionMaking)
```

boxplot(EmployeeSurvey$BudgetDecisionMaking)
```{r}
boxplot(EmployeeSurvey$BudgetDecisionMaking)
```
boxplot(EmployeeSurvey$BudgetDecisionMaking)

```{r}
boxplot(EmployeeSurvey$Organization)
```

boxplot(EmployeeSurvey$Organization)
```{r}
boxplot(EmployeeSurvey$JobImpact)
```
boxplot(EmployeeSurvey$JobImpact)

```{r}
boxplot(EmployeeSurvey$Workplace)
```
boxplot(EmployeeSurvey$Workplace)

```{r}
# Graphing

barplot(EmployeeSurvey$Age, main = "Age of Employees", xlab = "Employees", ylab = "Age", col = "Blue")
```

barplot(EmployeeSurvey$Age, main = "Age of Employees", xlab = "Employees", ylab = "Age", col = "Blue")
```{r}
barplot(EmployeeSurvey$Gender, main = "Gender of Employees", xlab = "Employees", ylab = "Gender", col = "Green")
```

barplot(EmployeeSurvey$Gender, main = "Gender of Employees", xlab = "Employees", ylab = "Gender", col = "Green")
```{r}
barplot(EmployeeSurvey$JobSatisfaction, main = "Satisfaction Level", xlab = "Employees", ylab = "Satisfaction", col = "Yellow")
```
barplot(EmployeeSurvey$JobSatisfaction, main = "Satisfaction Level", xlab = "Employees", ylab = "Satisfaction", col = "Yellow")

```{r}
barplot(EmployeeSurvey$ImpCharacteristics, main = "Job Characteristics", xlab = "Employees", ylab = "Characteristics", col = "Grey")
```

barplot(EmployeeSurvey$ImpCharacteristics, main = "Job Characteristics", xlab = "Employees", ylab = "Characteristics", col = "Grey")
```{r}
barplot(EmployeeSurvey$YearsinJob, main = "Years in the Job", xlab = "Employees", ylab = "Years", col = "Pink")
```
barplot(EmployeeSurvey$YearsinJob, main = "Years in the Job", xlab = "Employees", ylab = "Years", col = "Pink")

```{r}
hist(EmployeeSurvey$Promotion, main = "Promotion Level", xlab = "Employees", ylab = "Promotion", col = "Red")
```

hist(EmployeeSurvey$Promotion, main = "Promotion Level", xlab = "Employees", ylab = "Promotion", col = "Red")
```{r}
hist(EmployeeSurvey$DecisionMaking, main = "Decision Level", xlab = "Employees", ylab = "Decision Making", col = "Orange")
```

hist(EmployeeSurvey$DecisionMaking, main = "Decision Level", xlab = "Employees", ylab = "Decision Making", col = "Orange")
```{r}
hist(EmployeeSurvey$BudgetDecisionMaking, main = "Budget Level", xlab = "Employees", ylab = "Budget Decision", col = "Purple")
```
hist(EmployeeSurvey$BudgetDecisionMaking, main = "Budget Level", xlab = "Employees", ylab = "Budget Decision", col = "Purple")

```{r}
hist(EmployeeSurvey$Organization, main = "Company", xlab = "Employees", ylab = "Organization", col = "White")
```

hist(EmployeeSurvey$Organization, main = "Company", xlab = "Employees", ylab = "Organization", col = "White")
```{r}
hist(EmployeeSurvey$JobImpact, main = "Impact Level", xlab = "Employees", ylab = "Impacation", col = "Brown")
```
hist(EmployeeSurvey$JobImpact, main = "Impact Level", xlab = "Employees", ylab = "Impacation", col = "Brown")

```{r}
hist(EmployeeSurvey$Workplace, main = "Place", xlab = "Employees", ylab = "Worplace", col = "Grey")
```

hist(EmployeeSurvey$Workplace, main = "Place", xlab = "Employees", ylab = "Worplace", col = "Grey")
```{r}


# Columns

EmployeeSurvey$Age <- as.factor(EmployeeSurvey$Age)
class(EmployeeSurvey$Age)
```
class(EmployeeSurvey$Age)

```{r}
EmployeeSurvey$Gender <- as.factor(EmployeeSurvey$Gender)
class(EmployeeSurvey$Gender)
```

class(EmployeeSurvey$Gender)
```{r}
EmployeeSurvey$YearsinJob <- as.factor(EmployeeSurvey$YearsinJob)
class(EmployeeSurvey$YearsinJob)
```
class(EmployeeSurvey$YearsinJob)

```{r}
str(EmployeeSurvey)
```
str(EmployeeSurvey)

```{r}
EmployeeSurvey$Age <- as.numeric(EmployeeSurvey$Age)
class(EmployeeSurvey$Age)
```
class(EmployeeSurvey$Age)

```{r}
EmployeeSurvey$Organization <- as.factor(EmployeeSurvey$Organization)
class(EmployeeSurvey$Organization)
```
class(EmployeeSurvey$Organization)

```{r}
str(EmployeeSurvey)
```
str(EmployeeSurvey)

```{r}



# Scatter Plots

plot(EmployeeSurvey$Age, EmployeeSurvey$Gender, main = "Age VS Gender", xlab = "Age", ylab = "Gender", col = "Blue")
```

plot(EmployeeSurvey$Age, EmployeeSurvey$Gender, main = "Age VS Gender", xlab = "Age", ylab = "Gender", col = "Blue")
```{r}
plot(x=EmployeeSurvey$Age,y=EmployeeSurvey$Gender, main = "Age VS Gender", xlab = "Age", ylab = "Gender")
```
plot(x=EmployeeSurvey$Age,y=EmployeeSurvey$Gender, main = "Age VS Gender", xlab = "Age", ylab = "Gender")

```{r}
plot(x=EmployeeSurvey$JobSatisfaction, y=EmployeeSurvey$YearsinJob, main = "Satisfaction Level VS Years in Job", xlab = "Job Satisfaction", ylab = "Years")
```
plot(x=EmployeeSurvey$JobSatisfaction, y=EmployeeSurvey$YearsinJob, main = "Satisfaction Level VS Years in Job", xlab = "Job Satisfaction", ylab = "Years")

```{r}
plot(x=EmployeeSurvey$DecisionMaking, y=EmployeeSurvey$BudgetDecisionMaking, main = "Budget VS Decision Making", xlab = "Decision Making", ylab = "Budget Decision making")
```
plot(x=EmployeeSurvey$DecisionMaking, y=EmployeeSurvey$BudgetDecisionMaking, main = "Budget VS Decision Making", xlab = "Decision Making", ylab = "Budget Decision making")

```{r}

